Testing the Evolution of the Correlations between Supermassive Black Holes and their Host Galaxies using Eight Strongly Lensed quasars

### 2020-05-19 manuscript/manuscript.tex
before test auto-aff

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[X. Ding et al.]{
Xuheng Ding$^{1}$\thanks{E-mail: dxh@astro.ucla.edu},
Tommaso Treu$^{1}$,
Simon Birrer$^{2}$,
Adriano Agnello$^{3}$,\newauthor
Dominique Sluse$^{4}$,
Chris Fassnacht$^{5}$,
Matthew W. Auger$^{6}$,
Kenneth C. Wong$^{7}$, \newauthor
Sherry H. Suyu$^{8,9,10}$,
Takahiro Morshita$^{11}$,
and et al.
\\
\\
% List of institutions
$^{1}$Department of Physics and Astronomy, University of California, Los Angeles, CA, 90095-1547, USA\\
$^{2}$Kavli Institute for Particle Astrophysics and Cosmology and Department of Physics, Stanford University, Stanford, CA 94305, USA\\
$^{3}$European Southern Observatory, Karl-Schwarzschild-Strasse 2, 85748 Garching, Germany\\
$^{4}$STAR Institute, Quartier Agora - All\'ee du six Ao\^ut, 19c B-4000 Li\`ege, Belgium\\
$^{5}$Department of Physics, University of California, Davis, CA 95616, USA\\
$^{6}$Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3 0HA, UK\\
$^{7}$Kavli IPMU (WPI), UTIAS, The University of Tokyo, Kashiwa, Chiba 277-8583, Japan\\
$^{8}$Max-Planck-Institut f{\"u}r Astrophysik, Karl-Schwarzschild-Str.~1, 85748 Garching, Germany\\
$^{9}$Physik-Department, Technische Universit\"at M\"unchen, James-Franck-Stra\ss{}e~1, 85748 Garching, Germany\\
$^{10}$Academia Sinica Institute of Astronomy and Astrophysics (ASIAA), 11F of ASMAB, No.1, Section 4, Roosevelt Road, Taipei 10617, Taiwan\\
$^{11}$Space Telescope Science Institute, 3700 San Martin Drive, Baltimore, MD 21218, USA
$^{11}$TBC
}

@@

%%%%%%%%%%%%%%%%% BODY OF PAPER %%%%%%%%%%%%%%%%%%
\section{Introduction}
The tight correlations between the masses (\mbh) of supermassive black holes (BHs) and their host galaxies properties including stellar mass (\mstar), stellar velocity dispersion ($\sigma_*$) and luminosity (\lhost), known as scaling relations, are usually considered as a result of their co-evolution ~\citep[e.g.,][]{Mag++98, F+M00, Geb++01b, M+H03, Gul++09,Beifi2012, H+R04, Gra++2011}. Cosmological simulations of structure formation are able to reproduce the local tight relation based on physical mechanism by invoking active galactic nucleus (AGN) feedback as the physical connection~\citep{Springel2005, Hopkins2008, Matteo2008, DeG++15} or having them share a common gas supply~\citep{Cen2015, Menci2016}. However, it has also been suggested that the correlations arise statistically, without any physical coupling, as a result of stochastic megers~\citep{Peng2007, Jahnke2011, Hirschmann2010}.

@@

It has been long recognized that lensed AGNs, by virtue of magnification, can provide unique insights inro the scaling relations the distant universe~\citep{Peng2006}, provided that the lens modelling could be accurately derived. Aiming at verifying the fidelity of the modern lens modelling technique, \citet{Ding2017a} carried out extensive and realistic simulations tests based on the deep \hst\ observations for a sample of eight lens systems in the \hc\ Lenses in COSMOGRAIL's Wellspring (H0LiCOW, PI: Suyu) collaboration. They confirm that the reconstruction of the lensed host galaxy properties can be recovered with better precision and accuracy than the typical \mbh\ uncertainty. Then, \citet{Ding2017b} applied the advanced techniques to two strongly lensed systems analyzed by the H0LiCOW collaboration~\citep{Suyu2013, Wong2017} to study their \mbh-\lhost\ relations and obtained consistent scaling relations compared with the samples from the literature.

In this work, we expand the measurements of the \mbh-\mstar\ relation using the full sample of eight lensed AGN introduced by \citet{Ding2017a}.  In order to take advantage of the excellent quality of the data, we develop an independent approach to achieve a one-step inference of the host galaxy photometry from the eight lensed AGNs. We adopt a set of extended modelling choices to assure the accuracy of our measurements. We compare the inference of our new measurements to the ones which have been modelled by the H0LiCOW collaboration to make the cross-check. To assess an accurate inference of stellar mass, we utilize the imaging data taken with the \hst\ multi-band filter to obtain the color information for 3/8 of our targets. Furthermore, we adopt a class of self-consistent recipes to recalibrate the \mbh\ of our sample, in a manner consistent with D20. Given the similar redshift range, the high data quality, and consistent state of the art techniques, this sample of lensed AGN provides an excellent verfication of the D20 results.

This paper is structured as follows. In Section~\ref{sec:sample_select}, we introduce the sample including their imaging data and the BH masses. In Section~\ref{sec:lens_model}, we describe our approach designed to infer the lens models and reconstruct the host galaxy. We use the inferred photometry to derive the stellar mass and the scaling relations and combine with D20 sample to study the evolution in Section~\ref{sec:result}. Discussion and conclusions are drawn in Section~\ref{sec:diss} and~\ref{sec:con}. Throughout this paper, we adopt a standard concordance cosmology with parameters adopted as $H_0= 70$ km s$^{-1}$ Mpc$^{-1}$, $\Omega{_m} = 0.30$, and $\Omega{_\Lambda} = 0.70$. Magnitudes are presented in the AB system. A Chabrier initial mass function (IMF) is employed for the sample, consistently with D20.

\section{Sample Selection and Black Hole Mass Estimates}\label{sec:sample_select}
We adopt eight lens systems from our H0LiCOW collaboration including HE~0435$-$1223, RXJ~1131$-$1231, WFI~2033$-$4723, HE~1104$-$1805, SDSS~1206$+$4332, SDSS~0246$-$0825, HE~0047$-$1756 and HS~2209$+$1914. We refer to~\citet{Suyu2017, Ding2017a} for the descriptions of these data. We summarized the information for the eight systems, including their redshift and data conditions in Table~\ref{data_set}.
For conciseness, in the rest of this paper, we abbreviate each lens name to four digits (e.g., HE0435$-$1223 to HE0435).

@@

To ensure the consistency of \mbh\ estimates based on different broad lines, we adopt a the following set of self-consistent recipes following D20:
\begin{eqnarray}
\label{recipe}
\log \left(\frac{\mathcal M_{\rm BH}}{M_{\odot}}\right)&~=~& a+b \log \left(\frac{ \rm L _{\lambda_{line}}}{10^{44}{\rm erg~s^{-1}}}\right) \nonumber\\
&~+~& 2 \log \left(\frac{\rm FWHM(line)}{1000 ~{\rm km~s^{-1}}}\right) , 
\end {eqnarray}
%
with $a$\{\Civ, \Mgii, \Hb\}=\{6.322, 6.623, 6.910\},
$b$\{\Civ, \Mgii, \Hb\}=\{0.53, 0.47, 0.50\},
$\lambda_{line}$\{\Civ, \Mgii, \Hb\}=\{1350, 3000, 5100\}.
%
The broad line properties of our samples are adopted from the literature, with a few corrections/exceptions. % \citep{Sluse2012, Peng2006, Shen2011}.
The line properties of SDSS1206 have been inferred by~\citet{Shen2011}. However, this system was investigated as a non-lensed AGN and the lensing magnification on the intrinsic continuum luminosity was not considered. We follow~\citet{Birrer2019} and apply the same magnification correction on the $\log(L_\lambda)$ in this work. For the rest of the lens sample except HS2209, their broad line properties are adopted from the literature~\citep{Sluse2012, Peng2006} taking into account lensing magnification. For HS2209, the spectrum was observed at the Keck-II Telescope in September 2015. We derived the line properties from the spectrum using the same approach as~\citep{Sluse2012}. \todo{Dominique and Chris can give more details here.} . The \mbh\ measurements, together with the properties of the board-line are listed in Table~\ref{mbh}. 
The uncertainty of the \mbh\ are estimated to be $0.4$~dex.

\begin{table}
\centering
%\begin{threeparttable}
\caption{Summary of \mbh\ estimates, \pink{based on equation~\eqref{recipe}.}}\label{mbh}
\resizebox{8.5cm}{!}{
     \begin{tabular}{cccccc}
        \hline
Object ID & Line(s) & FWHM & log($L_\lambda$) & $\log$\mbh & ref.  \\
& & (\kms) & (${\rm erg~s^{-1}}$) & (M$_{\odot}$) \\ \hline
HE0435 & \Mgii & 4930 & 45.14 & 8.54 & (1) \\
RXJ1131 & \Mgii/\Hb & 5630/4545 & 44.29/44.02 & 8.26/8.23 & (1)\\
WFI2033 & \Mgii & 3960 & 45.19 & 8.38 & (1) \\
SDSS1206 & \Mgii & 5632 & 45.01 & 8.77 & (2) \\
HE1104 & \Civ & 6004 & 46.18 & 9.03 & (3) \\
SDSS0246 & \Mgii & 3700 & 45.19 & 8.32 & (1) \\
HS2209 & \Mgii & 3245 & 45.71 & 8.75 & \pink{here}  \\
HE0047 & \Mgii & 4145 & 45.59 & 8.60 & (1) \\
        \hline
     \end{tabular}
    }
\begin{tablenotes}
\small
\item Note: $-$ The broad line properties.\\ %For HS2209, the properties are derived in this work using the same approach as~\citet{Sluse2012}.
\pink{Reference: (1)~\citet{Sluse2012}, (2)~\citet{Shen2011}, (3)~\citet{Peng2006}.}\\
%$^a$: For SDSS1206, we follow~\citet{Birrer2019} and correct the AGN continuum luminosity $\log(L_\lambda$) by taking account the magnification effect {\bf [TT: how about the others?].}
\end{tablenotes}  
%\end{threeparttable}
\end{table}

\section{surface photometry inference}\label{sec:lens_model}
%
In this section, we describe how we derived surface photometry of the lensed galaxies taking lensing effects into account. Lens models of 4/8 systems, namely HE0435~\citep{Wong2017}, RXJ1131~\citep{Suyu2013}, WFI2033~\citep{Rusu2019} and SDSS1206~\citep{Birrer2019} have been published by the H0LiCOW project. The goal of those models was strong lens time-delay cosmography~\citep{Treu2016}, and the reconstruction of the host galaxy light (pixelized or via shapelets) was a byproduct. \citet{Ding2017b} used those reconstructions for two of the systems, including HE0435 and RXJ1131, and then fitted a simply parametrized surface brightness profile to the reconstruction to mimic what is done in non-lensed AGN.

In this work, in order to reproduce more closely and uniformly what is
done in non-lensed AGN we develope a strategy to obtain a one step
measurement of the host galaxy light described by a \sersic surface
brightness profile. For the 4/8 systems already studied by the H0LiCOW
project, we will make a comparison to characterize systematic
uncertainties related to modelling techniques.

@@

We following the standard procedure as described by D20 to prepare the fitting ingredients including the lensing imaging data, noise level map and the PSF information. The imaging data are first drizzled to a higher resolution with a Gaussian kernel; the adopted resolution are listed in Table~\ref{data_set}. We then adopt the {\sc Photutils} by Python to model the global background light in 2-D based on SExtractor algorithm. We remove the background light and cut the clear image data into postage stamp at a suitable size. We draw the image mask for each systems to define the region in which the pixels would to be used to calculate the likelihood; see the top-left panel in each subplot in Figure~\ref{fig:image_inference}.

We carry out a forward modelling process to simultaneously constrain the lens model, subtract the central AGN light, and infer the photometry of the host galaxy. For any extended objects, including the lensing galaxy and source galaxy, we assume their surface brightness can be described by the 2-D elliptical \sersic\ profile. We start with a single \sersic\ profile and consider to use two \sersic\ if any significant residual indicate a multiply component. For a single \sersic\ profile, we set the prior of the \sersic\ index value $n$ between $[0.5-5.0]$ to avoid unphysical results\footnote{It has been studied in~\citet{Ding2017a} that choosing the prior for \sersic\ index $n$ yields unbiased host magnitude inferences.}. The bright nucleus is unresolved and modelled by a scaled point spread function (PSF) in the image plane. We also impose that the AGN and its host galaxy have the same center. Following standard practice that has show to produce good models \citep[e.g.,][and references therein]{Treu2010}, we adopt elliptical Power-law density profiles to define the surface mass density of the deflector, with an external shear.

We employ the imaging modelling tool \lenstronomy\footnote{\url{https://github.com/sibirrer/lenstronomy}}~\citep{lenstronomy} to perform the fitting task. Inspired by D20, we adopt a set of extensive modelling choices to perform the fitting for each system. We then apply a statistical measurement and perform a weighting algorithm to derive the final inference and estimate the uncertainty level, including the contribution of modelling choices. The modelling choices that we consider include the follows.
\begin{enumerate}
\item Following common practice, we select all the bright, isolated stars across the image frame of targets to define the PSF. Each selected star is considered as an initial PSF guess for the fit.
\item The central pixels of the AGNs are very bright and can be affected by large systematic errors during the interpolation of the subsampled PSF. To avoid overfitting the noise, we adopt two different modelling options: 1)~manually boost the noise estimate in the central area to effectively infinite ({\it noise boost}); 2)~perform the iterative PSF estimation as introduced by~\citet{Chen2016, Birrer2019} ({\it PSF iteration}).
\item To calculate the ray tracing under a higher resolution grid, we chose to oversample the model by a factor  $2\times2$ or $3\times3$ pixel$^{-1}$.
\item Using the lensing imaging alone is difficult to constrain the power-law slope. To mitigate the overfitting of the slope value, we repeat the fit for three values $[1.9, 2.0, 2.1]$ that are meant to bracket the range observed in lens galaxies \citep[e.g.,][]{Auger2010}.
\end{enumerate}

In general, for one lens system with a number of $N$ initial PSF guesses, we perform in total $N\times12$ (i.e., $2 \times2 \times3$) fits. After all fits are completed, we rank their performance based on their best-fitted $\chi^2$ value. Since there is no evidence of an better performance for the options between {\it noise boost} and {\it PSF iteration}, we selected the top-4 fittings from each of them and then combine their best-fit results based on the weighting algorithm introduced by D20. The weights are defined by:
\begin{eqnarray}
\label{eq:weights}
w_i = exp \big(- \alpha \frac{ (\chi_i ^2 - \chi_{best} ^2 )}{2 \chi_{best} ^2} \big),
\end{eqnarray} 
where the $\alpha$ is an inflation parameter\footnote{Defining $\alpha$ as the {\it inflation} parameter it is assumed that it is larger than ~$1$, so as to err on the side of caution and include more choices that would be allowed strictly by statistical noise considerations.} so that when $i=4$:
\begin{eqnarray}
\label{eq:alpha}
\alpha \frac{ \chi_{i=4} ^2 - \chi_{best} ^2 }{2 \chi_{best} ^2} = 2.
\end{eqnarray} 
Then, the results by {\it noise boost} and {\it PSF iteration} are combined equally to derive the value of host properties and the root-mean-square error (i.e., $\sigma$ level) based on the weights of the $4+4$ (i.e., {\it noise boost} and {\it PSF iteration}) options by:
\begin{eqnarray}
\label{eq:infer_value}
\bar{x}  =  \frac{  \sum_{i=1}^{N}   x_i * w_i  }{\Sigma w_i} ,
\end{eqnarray} 
\begin{eqnarray}
\label{eq:infer_scatter}
\sigma =   \sqrt{ \frac{  \sum_{i=1}^{N}   (x_i -  \bar{x} ) ^2 * w_i  }{\Sigma w_i} }.
\end{eqnarray}

@@

\subsubsection{HE0435}
We follow the approach described in the previous section. We select 5 isolated stars in this field as initial PSFs to input to the fitting, for a total of 60 fits. Based on the top-eight choices, we perform the weighting algorithm and measure the host flux, host-to-total flux ratio, effective radius and \sersic\ index. The inference results are shown in Table~\ref{tab:host_measure}, (2)$-$(6) columns.

The inference by the best-fit lens model for HE0435 is shown in Figure~\ref{fig:image_inference}-(a). Not surprisingly, we note that the residuals level in the normalized plot appears to be larger than the ones presented by~\citet{Wong2017}. This is primarily due to the fact that the surface brightness of the host galaxy in our model is defined as the \sersic\ profile, which is relatively simple and smooth compare to the pixellated reconstruction technique adopted by {\sc Glee}~\citep{Suy++06, Halk2008, S+H10} or the shapelet technique adopted by \lenstronomy~\citep{Refregier2003, Birrer2015}. The smooth feature of \sersic\ profile could not capture the clumps in the host galaxy such as the star-forming regions. Nevertheless, our approach is sufficient to derive a self-consistent one-step inference of the global host light in terms of the \sersic\ flux, i.e. the quantity commonly measured in the the literature for non-lensed samples.

@@

\subsubsection{SDSS1206}
SDSS1206 is an unique system -- the AGN is a doubly imaged by the deflector while most of the host falls inside the inner caustic and ends up being quadruply imaged. Following~\citet{Birrer2019}, we consider the galaxy triplet group at the north-west and use a single SIS model to denote their overall mass perturbation. Moreover, as noted by~\citet{Birrer2019}, a sub-clump is located in the north which is hardly visible \citep[see Figure~1 in][]{Birrer2019}. We model this sub-clump as a SIS mass model and a circular \sersic\ light model with joint centroids. It is worth noting that we are using the same imaging modelling tool as~\citet{Birrer2019}.

@@

>>>>

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[X. Ding et al.]{
Xuheng Ding$^{1}$\thanks{E-mail: dxh@astro.ucla.edu},
Tommaso Treu$^{1}$,
Simon Birrer$^{2}$,
Adriano Agnello$^{3}$,\newauthor
Dominique Sluse$^{4}$,
Chris Fassnacht$^{5}$,
Matthew W. Auger$^{6}$,
Kenneth C. Wong$^{7}$, \newauthor
Sherry H. Suyu$^{8,9,10}$,
Takahiro Morshita$^{11}$,
Aymeric Galan$^{12}$,
and et al.
\\
\\
\\
% List of institutions
$^{1}$Department of Physics and Astronomy, University of California, Los Angeles, CA, 90095-1547, USA\\
$^{2}$Kavli Institute for Particle Astrophysics and Cosmology and Department of Physics, Stanford University, Stanford, CA 94305, USA\\
$^{3}$European Southern Observatory, Karl-Schwarzschild-Strasse 2, 85748 Garching, Germany\\
$^{4}$STAR Institute, Quartier Agora - All\'ee du six Ao\^ut, 19c B-4000 Li\`ege, Belgium\\
$^{5}$Department of Physics, University of California, Davis, CA 95616, USA\\
$^{6}$Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3 0HA, UK\\
$^{7}$Kavli IPMU (WPI), UTIAS, The University of Tokyo, Kashiwa, Chiba 277-8583, Japan\\
$^{8}$Max-Planck-Institut f{\"u}r Astrophysik, Karl-Schwarzschild-Str.~1, 85748 Garching, Germany\\
$^{9}$Physik-Department, Technische Universit\"at M\"unchen, James-Franck-Stra\ss{}e~1, 85748 Garching, Germany\\
$^{10}$Academia Sinica Institute of Astronomy and Astrophysics (ASIAA), 11F of ASMAB, No.1, Section 4, Roosevelt Road, Taipei 10617, Taiwan\\
$^{11}$Space Telescope Science Institute, 3700 San Martin Drive, Baltimore, MD 21218, USA\\
$^{12}$Institute of Physics, Laboratory of Astrophysics, Ecole Polytechnique 
F\'ed\'erale de Lausanne (EPFL), Observatoire de Sauverny, 1290 Versoix, 
Switzerland\\
$^{13}$TBC
}

@@

%%%%%%%%%%%%%%%%% BODY OF PAPER %%%%%%%%%%%%%%%%%%
\section{Introduction}
The tight correlations between the masses (\mbh) of supermassive black holes (BHs) and their host galaxies properties including stellar mass (\mstar), stellar velocity dispersion ($\sigma_*$) and luminosity (\lhost), known as scaling relations, are usually considered as a result of their co-evolution ~\citep[e.g.,][]{Mag++98, F+M00, Geb++01b, M+H03, Gul++09,Beifi2012, H+R04, Gra++2011}. Cosmological simulations of structure formation are able to reproduce the local tight relation based on physical mechanism by invoking active galactic nucleus (AGN) feedback as the physical connection~\citep{Springel2005, Hopkins2008, Matteo2008, DeG++15} or having them share a common gas supply~\citep{Cen2015, Menci2016}. However, it has also been suggested that the correlations arise statistically, without any physical coupling, as a result of stochastic mergers~\citep{Peng2007, Jahnke2011, Hirschmann2010}.

@@

It has been long recognized that lensed AGNs, by virtue of magnification, can provide unique insights into the scaling relations the distant universe~\citep{Peng2006}, provided that the lens modelling could be accurately derived. Aiming at verifying the fidelity of the modern lens modelling technique, \citet{Ding2017a} carried out extensive and realistic simulations tests based on the deep \hst\ observations for a sample of eight lens systems in the \hc\ Lenses in COSMOGRAIL's Wellspring (H0LiCOW\footnote{\url{http://www.h0licow.org/}}, PI: Suyu) collaboration. They confirm that the reconstruction of the lensed host galaxy properties can be recovered with better precision and accuracy than the typical \mbh\ uncertainty. Then, \citet{Ding2017b} applied the advanced techniques to two strongly lensed systems analyzed by the H0LiCOW collaboration~\citep{Suyu2013, Wong2017} to study their \mbh-\lhost\ relations and obtained consistent scaling relations compared with the samples from the literature.

In this work, we expand the measurements of the \mbh-\mstar\ relation using the full sample of eight lensed AGN introduced by \citet{Ding2017a}.  In order to take advantage of the excellent quality of the data, we develop an independent approach to achieve a one-step inference of the host galaxy photometry from the eight lensed AGNs. We adopt a set of extended modelling choices to assure the accuracy of our measurements. We compare the inference of our new measurements to the ones which have been modelled by the H0LiCOW collaboration to make the cross-check. To assess an accurate inference of stellar mass, we utilize the imaging data taken with the \hst\ multi-band filter to obtain the color information for 3/8 of our targets. Furthermore, we adopt a class of self-consistent recipes to recalibrate the \mbh\ of our sample, in a manner consistent with D20. Given the similar redshift range, the high data quality, and consistent state of the art techniques, this sample of lensed AGN provides an excellent verification of the D20 results.

This paper is structured as follows. In Section~\ref{sec:sample_select}, we introduce the sample including their imaging data and the BH masses. In Section~\ref{sec:lens_model}, we describe our approach designed to infer the lens models and reconstruct the host galaxy. We use the inferred photometry to derive the stellar mass and the scaling relations and combine with D20 sample to study the evolution in Section~\ref{sec:result}. Discussion and conclusions are drawn in Section~\ref{sec:diss} and~\ref{sec:con}. Throughout this paper, we adopt a standard concordance cosmology with parameters adopted as $H_0= 70$ km s$^{-1}$ Mpc$^{-1}$, $\Omega{_m} = 0.30$, and $\Omega{_\Lambda} = 0.70$, \pink{to compute the luminosity distance and estimate the host absolute brightness}. Magnitudes are presented in the AB system. A Chabrier initial mass function (IMF) is employed for the sample, consistently with D20.

\section{Sample Selection and Black Hole Mass Estimates}\label{sec:sample_select}
We adopt eight lens systems from our H0LiCOW collaboration including HE0435$-$1223, RXJ1131$-$1231, WFI2033$-$4723, HE1104$-$1805, SDSS1206$+$4332, SDSS0246$-$0825, HE0047$-$1756 and HS2209$+$1914. We refer to~\citet{Suyu2017, Ding2017a} for the descriptions of these data. We summarized the information for the eight systems, including their redshift and data conditions in Table~\ref{data_set}.
For conciseness, in the rest of this paper, we abbreviate each lens name to four digits (e.g., HE0435$-$1223 to HE0435).

@@

To ensure the consistency of \mbh\ estimates based on different broad lines, we adopt the following set of self-consistent recipes following D20:
\begin{eqnarray}
\label{recipe}
\log \left(\frac{\mathcal M_{\rm BH}}{M_{\odot}}\right)&~=~& a+b \log \left(\frac{ \rm L _{\lambda_{line}}}{10^{44}{\rm erg~s^{-1}}}\right) \nonumber\\
&~+~& 2 \log \left(\frac{\rm FWHM(line)}{1000 ~{\rm km~s^{-1}}}\right) , 
\end {eqnarray}
%
with $a$\{\Civ, \Mgii, \Hb\}=\{6.322, 6.623, 6.910\},
$b$\{\Civ, \Mgii, \Hb\}=\{0.53, 0.47, 0.50\},
$\lambda_{\rm line}$\{\Civ, \Mgii, \Hb\}=\{1350, 3000, 5100\}.
%
The broad line properties of our samples are adopted from the literature, with a few corrections/exceptions. % \citep{Sluse2012, Peng2006, Shen2011}.
The line properties of SDSS1206 have been inferred by~\citet{Shen2011}. However, this system was investigated as a non-lensed AGN and the lensing magnification on the intrinsic continuum luminosity was not considered. We follow~\citet{Birrer2019} and apply the same magnification correction on the $\log(L_\lambda)$ in this work. For the rest of the lens sample except HS2209, their broad line properties are adopted from the literature~\citep{Sluse2012, Peng2006} taking into account lensing magnification. For HS2209, the spectrum was observed at the Keck-II Telescope in September 2015. We derived the line properties from the spectrum using the same approach as~\citet{Sluse2012},\pink{ based on \Mgii}. \todo{Dominique and Chris can give more details here.} . The \mbh\ measurements, together with the properties of the board-line, are listed in Table~\ref{mbh}. 
The uncertainty of the \mbh\ are estimated to be $0.4$~dex.

\begin{table}
\centering
%\begin{threeparttable}
\caption{Summary of \mbh\ estimates, based on equation~\eqref{recipe}.}\label{mbh}
\resizebox{8.5cm}{!}{
     \begin{tabular}{cccccc}
        \hline
Object ID & Line(s) & FWHM & log($L_\lambda$) & $\log$\mbh & ref.  \\
& & (\kms) & (${\rm erg~s^{-1}}$) & (M$_{\odot}$) \\ \hline
HE0435 & \Mgii & 4930 & 45.14 & 8.54 & (1) \\
RXJ1131 & \Mgii/\Hb & 5630/4545 & 44.29/44.02 & 8.26/8.23 & (1)\\
WFI2033 & \Mgii & 3960 & 45.19 & 8.38 & (1) \\
SDSS1206 & \Mgii & 5632 & 45.01 & 8.77 & (2) \\
HE1104 & \Civ & 6004 & 46.18 & 9.03 & (3) \\
SDSS0246 & \Mgii & 3700 & 45.19 & 8.32 & (1) \\
HS2209 & \Mgii & 3245 & 45.71 & 8.75 & here  \\
HE0047 & \Mgii & 4145 & 45.59 & 8.60 & (1) \\
        \hline
     \end{tabular}
    }
\begin{tablenotes}
\small
\item Note: $-$ The broad line properties.\\ %For HS2209, the properties are derived in this work using the same approach as~\citet{Sluse2012}.
Reference: (1)~\citet{Sluse2012}, (2)~\citet{Shen2011}, (3)~\citet{Peng2006}.\\
%$^a$: For SDSS1206, we follow~\citet{Birrer2019} and correct the AGN continuum luminosity $\log(L_\lambda$) by taking account the magnification effect {\bf [TT: how about the others?].}
\end{tablenotes}  
%\end{threeparttable}
\end{table}

\section{surface photometry inference}\label{sec:lens_model}
%
In this section, we describe how we derived surface photometry of the lensed galaxies taking lensing effects into account. Lens models of 4/8 systems, namely HE0435~\citep{Wong2017}, RXJ1131~\citep{Suyu2013}, WFI2033~\citep{Rusu2019} and SDSS1206~\citep{Birrer2019} have been published by the H0LiCOW project. The goal of those models was strong lens time-delay cosmography~\citep{Treu2016}, and the reconstruction of the host galaxy light\pink{(via pixellated distribution~\citep{Suy++06} or shapelets~\citep{Refregier2003})} was a byproduct. \citet{Ding2017b} used those reconstructions for two of the systems (HE0435 and RXJ1131), and then fitted a simply parametrized surface brightness profile to the reconstruction to\pink{measure the host properties as the non-lensed AGN case}.
% mimic what is done in non-lensed AGN.

In this work, in order to reproduce more closely and uniformly what is
done in non-lensed AGN, we develop a strategy to obtain a one step
measurement of the host galaxy light described by a \sersic\ surface
brightness profile. For the 4/8 systems already studied by the H0LiCOW
project, we will make a comparison to characterize systematic
uncertainties related to modelling techniques.

@@

We follow the standard procedure as described by D20 to prepare the fitting ingredients including the lensing imaging data, noise level map and the PSF information. The imaging data are first drizzled to a higher resolution with a Gaussian kernel; the adopted resolution are listed in Table~\ref{data_set}. We then adopt the {\sc Photutils}~\citep{photutils} by Python to model the global background light in 2-D based on \texttt{SExtractor} algorithm. We remove the background light and cut the clear image data into postage stamp at a suitable size. We draw the image mask for each systems to define the region in which the pixels are used to calculate the likelihood; see the top-left panel in each subplot in Figure~\ref{fig:image_inference}.

We carry out a forward modelling process to simultaneously constrain the lens model, subtract the central AGN light, and infer the photometry of the host galaxy. For any extended objects, including the lensing galaxy and source galaxy, we assume their surface brightness can be described by the 2-D elliptical \sersic\ profile. We start with a single \sersic\ profile and consider to use two \sersic\ if any significant residual indicate a multiple component. For a single \sersic\ profile, we set the prior of the \sersic\ index value $n$ between $[0.5-5.0]$ to avoid unphysical results\footnote{It has been studied in~\citet{Ding2017a} that choosing the prior for \sersic\ index $n$ yields unbiased host magnitude inferences.}. The bright nucleus is unresolved and modelled by a scaled point spread function (PSF) in the image plane. We also impose that the AGN and its host galaxy have the same center. Following standard practice that has show to produce good models \citep[e.g.,][and references therein]{Treu2010}, we adopt elliptical Power-law density profiles to define the surface mass density of the deflector, with an external shear.

We employ the imaging modelling tool \lenstronomy\footnote{\url{https://github.com/sibirrer/lenstronomy}}~\citep{lenstronomy} to perform the fitting task. Inspired by D20, we adopt a set of extensive modelling choices to perform the fitting\pink{ for each system, repeatedly. Then, based on the fittings using different choices,} we apply a statistical measurement and perform a weighting algorithm to derive the final inference and estimate the uncertainty \pink{level}. The modelling choices that we consider include the follows.
\begin{enumerate}
\item Following common practice, we select all the bright, isolated stars across the image frame of targets to define the PSF. Each selected star is considered as an initial PSF guess for the fit.
\item The central pixels of the AGNs are very bright and can be affected by large systematic errors during the interpolation of the subsampled PSF. To avoid overfitting the noise, we adopt two different modelling options: 1)~manually boost the noise estimate in the central area to effectively infinite ({\it noise boost}); 2)~perform the iterative PSF estimation as introduced by~\citet{Chen2016, Birrer2019} ({\it PSF iteration}).
\item To calculate the ray tracing under a higher resolution grid, we chose to oversample the model by a factor  $2\times2$ or $3\times3$ pixel$^{-1}$.
\item Using the lensing imaging alone is difficult to constrain the power-law slope, \pink{especially the model of our host surface brightness is much simplified}. To mitigate the overfitting of the slope value, we repeat the fit for three values $[1.9, 2.0, 2.1]$ that are meant to bracket the range observed in lens galaxies \citep[e.g.,][]{Auger2010}.
\end{enumerate}

In general, for one lens system with a number of $N$ initial PSF guesses, we perform in total $N\times12$ (i.e., $2 \times2 \times3$) fits. After all fits are completed, we rank their performance based on their best-fitted $\chi^2$ value. Since there is no evidence of a better performance for the options between {\it noise boost} and {\it PSF iteration}, we selected the top-4 fittings from each of them and then combine their best-fit results based on the weighting algorithm introduced by D20. The weights are defined by:
\begin{eqnarray}
\label{eq:weights}
w_i = {\rm exp} \big(- \alpha \frac{ (\chi_i ^2 - \chi_{best} ^2 )}{2 \chi_{best} ^2} \big),
\end{eqnarray} 
where the $\alpha$ is an inflation parameter\footnote{Defining $\alpha$ as the {\it inflation} parameter it is assumed that it is larger than ~$1$, so as to err on the side of caution and include more choices that would be allowed strictly by statistical noise considerations.} so that when $i=4$:
\begin{eqnarray}
\label{eq:alpha}
\alpha \frac{ \chi_{i=4} ^2 - \chi_{best} ^2 }{2 \chi_{best} ^2} = 2.
\end{eqnarray} 
Then, the results by {\it noise boost} and {\it PSF iteration} are combined equally to derive the value of host properties and the root-mean-square error (i.e., $\sigma$ level) based on the weights of the $4+4$ (i.e., {\it noise boost} and {\it PSF iteration}) options by:
\begin{eqnarray}
\label{eq:infer_value}
\bar{x}  =  \frac{  \sum_{i=1}^{N}   x_i * w_i  }{\Sigma w_i} ,
\end{eqnarray} 
\begin{eqnarray}
\label{eq:infer_scatter}
\sigma =   \sqrt{ \frac{  \sum_{i=1}^{N}   (x_i -  \bar{x} ) ^2 * w_i  }{\Sigma w_i} }.
\end{eqnarray}

@@

\subsubsection{HE0435}\label{subsec:HE0435}
We follow the approach described in the previous section. We select 5 isolated stars in this field as initial PSFs to input to the fitting, for a total of 60 fits. Based on the top-eight choices, we perform the weighting algorithm and measure the host flux, host-to-total flux ratio, effective radius and \sersic\ index. The inference results are shown in Table~\ref{tab:host_measure}, (2)$-$(6) columns.

The inference by the best-fit lens model for HE0435 is shown in Figure~\ref{fig:image_inference}-(a). Not surprisingly, we note that the residuals level in the normalized plot appears to be larger than the ones presented by~\citet{Wong2017}. This is primarily due to the fact that the surface brightness of the host galaxy in our model is defined as the \sersic\ profile, which is relatively simple and smooth compare to the pixellated reconstruction technique adopted by {\sc Glee}~\citep{Suy++06, Halk2008, S+H10} or the shapelet technique adopted by \lenstronomy~\citep{Birrer2015}. The smooth feature of \sersic\ profile could not capture the clumps in the host galaxy such as the star-forming regions. Nevertheless, our approach is sufficient to derive a self-consistent one-step inference of the global host light in terms of the \sersic\ flux, i.e. the quantity commonly measured in the literature for non-lensed samples.

@@

\subsubsection{SDSS1206}
SDSS1206 is a unique system -- the AGN is doubly imaged by the deflector while most of the host falls inside the inner caustic and ends up being quadruply imaged. Following~\citet{Birrer2019}, we consider the galaxy triplet group at the north-west and use a single SIS model to denote their overall mass perturbation. Moreover, as noted by~\citet{Birrer2019}, a sub-clump is located in the north which is hardly visible \citep[see Figure~1 in][]{Birrer2019}. We model this sub-clump as a SIS mass model and a circular \sersic\ light model with joint centroids. It is worth noting that we are using the same imaging modelling tool as~\citet{Birrer2019}.

@@

\pink{The strong lensing can help to extend the measurements of the AGN host to even higher redshift. It is worth noting that the lensed AGN adopted by this study are adopted from the H0LiCOW project which only focuses on the moment of the peak of the AGN luminosity function. In fact, the observation of \hst\ could even unveil the lensed AGN host of  BRI0952$-$0115 at $z=4.5$.}
